---
title: "Drobonin Model Prediction"
author: "Lucy Whitmore"
date: "10/6/2023"
output: html_document
---

User notes: this script should be able to make predictions based on the Drobonin et al., 2022 BrainAGE model. The script is currently set up to predict for 2 waves of data, baseline and follow-up (ABCD 2 year followup).

In order to run predictions, you'll need 2 things: the xgboost model, available at https://github.com/GitDro/DevelopmentalBrainAge/blob/master/model/xgboost_9to19_brain_age_mod.rds, and a data frame. The dataframe should have only interview age (in years) and columns for brain measures. IDs can be reattached after predictions are made, the rows won't change in order.

```{r}
library(tidymodels)
library(xgboost) 
```
Code for renaming columns
```{r} 
# The following code should rename ABCD smri variables to match the Drobonin model. Note, not all the features from the model exist in ABCD, so we also have to make empty columns for those.


renamed_smri_baseline <- smri_baseline %>% 
  rename(FS_InterCranial_Vol = smri_vol_scs_intracranialv, #technically inter vs intra
#FS_BrainSeg_Vol
#FS_BrainSeg_Vol_No_Vent
#FS_BrainSeg_Vol_No_Vent_Surf
FS_LCort_GM_Vol = smri_vol_cdk_totallh,
FS_RCort_GM_Vol = smri_vol_cdk_totalrh,
FS_TotCort_GM_Vol = smri_vol_cdk_total, #total whole brain cortical volume
FS_SubCort_GM_Vol = smri_vol_scs_subcorticalgv,
#FS_Total_GM_Vol #maybe just calculate?
FS_SupraTentorial_Vol = smri_vol_scs_suprateialv, #assuming this includes all ventricles
#FS_SupraTentorial_Vol_No_Vent  #smri_vol_scs_allventricles is all ventricles, subtract?
#FS_SupraTentorial_No_Vent_Voxel_Count
#FS_Mask_Vol
#FS_BrainSegVol_eTIV_Ratio
#FS_MaskVol_eTIV_Ratio
FS_L_LatVent_Vol = smri_vol_scs_ltventriclelh,
FS_L_InfLatVent_Vol = smri_vol_scs_inflatventlh,
FS_L_Cerebellum_WM_Vol = smri_vol_scs_crbwmatterlh,
FS_L_Cerebellum_Cort_Vol = smri_vol_scs_crbcortexlh,
FS_L_ThalamusProper_Vol = smri_vol_scs_tplh,
FS_L_Caudate_Vol = smri_vol_scs_caudatelh,
FS_L_Putamen_Vol = smri_vol_scs_putamenlh,
FS_L_Pallidum_Vol = smri_vol_scs_pallidumlh,
FS_3rdVent_Vol = smri_vol_scs_3rdventricle,
FS_4thVent_Vol = smri_vol_scs_4thventricle,
FS_BrainStem_Vol = smri_vol_scs_bstem,
FS_L_Hippo_Vol = smri_vol_scs_hpuslh,
FS_L_Amygdala_Vol =	smri_vol_scs_amygdalalh,
FS_CSF_Vol = smri_vol_scs_csf,
FS_L_AccumbensArea_Vol = smri_vol_scs_aal,
FS_L_VentDC_Vol = smri_vol_scs_vedclh,
#FS_L_Vessel_Vol
#FS_L_ChoroidPlexus_Vol
FS_R_LatVent_Vol = 	smri_vol_scs_ltventriclerh,
FS_R_InfLatVent_Vol = smri_vol_scs_inflatventrh,
FS_R_Cerebellum_WM_Vol = smri_vol_scs_crbwmatterrh,
FS_R_Cerebellum_Cort_Vol = smri_vol_scs_crbcortexrh,
FS_R_ThalamusProper_Vol = smri_vol_scs_tprh,
FS_R_Caudate_Vol = smri_vol_scs_caudaterh,
FS_R_Putamen_Vol = smri_vol_scs_putamenrh,
FS_R_Pallidum_Vol = smri_vol_scs_pallidumrh,
FS_R_Hippo_Vol = smri_vol_scs_hpusrh,
FS_R_Amygdala_Vol = smri_vol_scs_amygdalarh,
FS_R_AccumbensArea_Vol = 	smri_vol_scs_aar,
FS_R_VentDC_Vol = smri_vol_scs_vedcrh,
#FS_R_Vessel_Vol
#FS_R_ChoroidPlexus_Vol
#FS_OpticChiasm_Vol
FS_CC_Posterior_Vol = smri_vol_scs_ccps,
FS_CC_MidPosterior_Vol = smri_vol_scs_ccmidps,
FS_CC_Central_Vol = smri_vol_scs_ccct,
FS_CC_MidAnterior_Vol = smri_vol_scs_ccmidat,
FS_CC_Anterior_Vol = smri_vol_scs_ccat,
FS_L_Bankssts_Area = 	smri_area_cdk_banksstslh,
FS_L_Caudalanteriorcingulate_Area = smri_area_cdk_cdacatelh,
FS_L_Caudalmiddlefrontal_Area = smri_area_cdk_cdmdfrlh,
FS_L_Cuneus_Area = 	smri_area_cdk_cuneuslh,
FS_L_Entorhinal_Area = smri_area_cdk_ehinallh,
FS_L_Fusiform_Area = smri_area_cdk_fusiformlh,
FS_L_Inferiorparietal_Area = smri_area_cdk_ifpllh,
FS_L_Inferiortemporal_Area = smri_area_cdk_iftmlh,
FS_L_Isthmuscingulate_Area = smri_area_cdk_ihcatelh,
FS_L_Lateraloccipital_Area = smri_area_cdk_locclh,
FS_L_Lateralorbitofrontal_Area = smri_area_cdk_lobfrlh,
FS_L_Lingual_Area = smri_area_cdk_linguallh,
FS_L_Medialorbitofrontal_Area = smri_area_cdk_mobfrlh,
FS_L_Middletemporal_Area = smri_area_cdk_mdtmlh,
FS_L_Parahippocampal_Area = smri_area_cdk_parahpallh,
FS_L_Paracentral_Area = smri_area_cdk_paracnlh,
FS_L_Parsopercularis_Area = smri_area_cdk_parsopclh,
FS_L_Parsorbitalis_Area = smri_area_cdk_parsobislh,
FS_L_Parstriangularis_Area = smri_area_cdk_parstgrislh,
FS_L_Pericalcarine_Area = smri_area_cdk_pericclh,
FS_L_Postcentral_Area = smri_area_cdk_postcnlh,
FS_L_Posteriorcingulate_Area = smri_area_cdk_ptcatelh,
FS_L_Precentral_Area = smri_area_cdk_precnlh,
FS_L_Precuneus_Area = smri_area_cdk_pclh,
FS_L_Rostralanteriorcingulate_Area = smri_area_cdk_rracatelh,
FS_L_Rostralmiddlefrontal_Area = smri_area_cdk_rrmdfrlh,
FS_L_Superiorfrontal_Area = smri_area_cdk_sufrlh,
FS_L_Superiorparietal_Area = smri_area_cdk_supllh,
FS_L_Superiortemporal_Area = smri_area_cdk_sutmlh,
FS_L_Supramarginal_Area = smri_area_cdk_smlh,
FS_L_Frontalpole_Area = smri_area_cdk_frpolelh,
FS_L_Temporalpole_Area = smri_area_cdk_tmpolelh,
FS_L_Transversetemporal_Area = smri_area_cdk_trvtmlh,
FS_L_Insula_Area = smri_area_cdk_insulalh,
FS_R_Bankssts_Area = smri_area_cdk_banksstsrh,
FS_R_Caudalanteriorcingulate_Area = smri_area_cdk_cdacaterh,
FS_R_Caudalmiddlefrontal_Area = smri_area_cdk_cdmdfrrh,
FS_R_Cuneus_Area = smri_area_cdk_cuneusrh,
FS_R_Entorhinal_Area = smri_area_cdk_ehinalrh,
FS_R_Fusiform_Area = smri_area_cdk_fusiformrh,
FS_R_Inferiorparietal_Area = smri_area_cdk_ifplrh,
FS_R_Inferiortemporal_Area = 	smri_area_cdk_iftmrh,
FS_R_Isthmuscingulate_Area = smri_area_cdk_ihcaterh,
FS_R_Lateraloccipital_Area = smri_area_cdk_loccrh,
FS_R_Lateralorbitofrontal_Area = smri_area_cdk_lobfrrh,
FS_R_Lingual_Area = smri_area_cdk_lingualrh,
FS_R_Medialorbitofrontal_Area = smri_area_cdk_mobfrrh,
FS_R_Middletemporal_Area = smri_area_cdk_mdtmrh,
FS_R_Parahippocampal_Area = smri_area_cdk_parahpalrh,
FS_R_Paracentral_Area = smri_area_cdk_paracnrh,
FS_R_Parsopercularis_Area = smri_area_cdk_parsopcrh,
FS_R_Parsorbitalis_Area = smri_area_cdk_parsobisrh,
FS_R_Parstriangularis_Area = smri_area_cdk_parstgrisrh,
FS_R_Pericalcarine_Area = smri_area_cdk_periccrh,
FS_R_Postcentral_Area = smri_area_cdk_postcnrh,
FS_R_Posteriorcingulate_Area = smri_area_cdk_ptcaterh,
FS_R_Precentral_Area = smri_area_cdk_precnrh,
FS_R_Precuneus_Area = smri_area_cdk_pcrh,
FS_R_Rostralanteriorcingulate_Area = smri_area_cdk_rracaterh,
FS_R_Rostralmiddlefrontal_Area = smri_area_cdk_rrmdfrrh,
FS_R_Superiorfrontal_Area = smri_area_cdk_sufrrh,
FS_R_Superiorparietal_Area = 	smri_area_cdk_suplrh,
FS_R_Superiortemporal_Area = smri_area_cdk_sutmrh,
FS_R_Supramarginal_Area = smri_area_cdk_smrh,
FS_R_Frontalpole_Area = smri_area_cdk_frpolerh,
FS_R_Temporalpole_Area = smri_area_cdk_tmpolerh,
FS_R_Transversetemporal_Area = smri_area_cdk_trvtmrh,
FS_R_Insula_Area = smri_area_cdk_insularh,
#abcd technically doesn't say gray matter volume for the following varibles
FS_L_Bankssts_GrayVol = smri_vol_cdk_banksstslh,
FS_L_Caudalanteriorcingulate_GrayVol = smri_vol_cdk_cdacatelh,
FS_L_Caudalmiddlefrontal_GrayVol = smri_vol_cdk_cdmdfrlh,
FS_L_Cuneus_GrayVol = smri_vol_cdk_cuneuslh,
FS_L_Entorhinal_GrayVol = smri_vol_cdk_ehinallh,
FS_L_Fusiform_GrayVol = smri_vol_cdk_fusiformlh,
FS_L_Inferiorparietal_GrayVol = smri_vol_cdk_ifpllh,
FS_L_Inferiortemporal_GrayVol = smri_vol_cdk_iftmlh,
FS_L_Isthmuscingulate_GrayVol = smri_vol_cdk_ihcatelh,
FS_L_Lateraloccipital_GrayVol = smri_vol_cdk_locclh,
FS_L_Lateralorbitofrontal_GrayVol = smri_vol_cdk_lobfrlh,
FS_L_Lingual_GrayVol = smri_vol_cdk_linguallh,
FS_L_Medialorbitofrontal_GrayVol = smri_vol_cdk_mobfrlh,
FS_L_Middletemporal_GrayVol = smri_vol_cdk_mdtmlh,
FS_L_Parahippocampal_GrayVol = smri_vol_cdk_parahpallh,
FS_L_Paracentral_GrayVol = smri_vol_cdk_paracnlh,
FS_L_Parsopercularis_GrayVol = smri_vol_cdk_parsopclh,
FS_L_Parsorbitalis_GrayVol = smri_vol_cdk_parsobislh,
FS_L_Parstriangularis_GrayVol = smri_vol_cdk_parstgrislh,
FS_L_Pericalcarine_GrayVol = smri_vol_cdk_pericclh,
FS_L_Postcentral_GrayVol = smri_vol_cdk_postcnlh,
FS_L_Posteriorcingulate_GrayVol = smri_vol_cdk_ptcatelh,
FS_L_Precentral_GrayVol = smri_vol_cdk_precnlh,
FS_L_Precuneus_GrayVol = smri_vol_cdk_pclh,
FS_L_Rostralanteriorcingulate_GrayVol = smri_vol_cdk_rracatelh,
FS_L_Rostralmiddlefrontal_GrayVol = smri_vol_cdk_rrmdfrlh,
FS_L_Superiorfrontal_GrayVol = smri_vol_cdk_sufrlh,
FS_L_Superiorparietal_GrayVol = smri_vol_cdk_supllh,
FS_L_Superiortemporal_GrayVol = smri_vol_cdk_sutmlh,
FS_L_Supramarginal_GrayVol = smri_vol_cdk_smlh,
FS_L_Frontalpole_GrayVol = smri_vol_cdk_frpolelh,
FS_L_Temporalpole_GrayVol = smri_vol_cdk_tmpolelh,
FS_L_Transversetemporal_GrayVol = smri_vol_cdk_trvtmlh,
FS_L_Insula_GrayVol = smri_vol_cdk_insulalh,
FS_R_Bankssts_GrayVol = smri_vol_cdk_banksstsrh,
FS_R_Caudalanteriorcingulate_GrayVol = smri_vol_cdk_cdacaterh,
FS_R_Caudalmiddlefrontal_GrayVol = 	smri_vol_cdk_cdmdfrrh,
FS_R_Cuneus_GrayVol = smri_vol_cdk_cuneusrh,
FS_R_Entorhinal_GrayVol = smri_vol_cdk_ehinalrh,
FS_R_Fusiform_GrayVol = smri_vol_cdk_fusiformrh,
FS_R_Inferiorparietal_GrayVol = smri_vol_cdk_ifplrh,
FS_R_Inferiortemporal_GrayVol = smri_vol_cdk_iftmrh,
FS_R_Isthmuscingulate_GrayVol = smri_vol_cdk_ihcaterh,
FS_R_Lateraloccipital_GrayVol = smri_vol_cdk_loccrh,
FS_R_Lateralorbitofrontal_GrayVol = smri_vol_cdk_lobfrrh,
FS_R_Lingual_GrayVol = smri_vol_cdk_lingualrh,
FS_R_Medialorbitofrontal_GrayVol = smri_vol_cdk_mobfrrh,
FS_R_Middletemporal_GrayVol = smri_vol_cdk_mdtmrh,
FS_R_Parahippocampal_GrayVol = smri_vol_cdk_parahpalrh,
FS_R_Paracentral_GrayVol = smri_vol_cdk_paracnrh,
FS_R_Parsopercularis_GrayVol = smri_vol_cdk_parsopcrh,
FS_R_Parsorbitalis_GrayVol = smri_vol_cdk_parsobisrh,
FS_R_Parstriangularis_GrayVol = smri_vol_cdk_parstgrisrh,
FS_R_Pericalcarine_GrayVol = smri_vol_cdk_periccrh,
FS_R_Postcentral_GrayVol = smri_vol_cdk_postcnrh,
FS_R_Posteriorcingulate_GrayVol = 	smri_vol_cdk_ptcaterh,
FS_R_Precentral_GrayVol = smri_vol_cdk_precnrh,
FS_R_Precuneus_GrayVol = smri_vol_cdk_pcrh,
FS_R_Rostralanteriorcingulate_GrayVol = smri_vol_cdk_rracaterh,
FS_R_Rostralmiddlefrontal_GrayVol = smri_vol_cdk_rrmdfrrh,
FS_R_Superiorfrontal_GrayVol = smri_vol_cdk_sufrrh,
FS_R_Superiorparietal_GrayVol = smri_vol_cdk_suplrh,
FS_R_Superiortemporal_GrayVol = smri_vol_cdk_sutmrh,
FS_R_Supramarginal_GrayVol = smri_vol_cdk_smrh,
FS_R_Frontalpole_GrayVol = smri_vol_cdk_frpolerh,
FS_R_Temporalpole_GrayVol = smri_vol_cdk_tmpolerh,
FS_R_Transversetemporal_GrayVol = smri_vol_cdk_trvtmrh,
FS_R_Insula_GrayVol = smri_vol_cdk_insularh
)


#Create empty columns to match feature list
renamed_smri_baseline[,"FS_BrainSeg_Vol"] <- NA
renamed_smri_baseline[,"FS_BrainSeg_Vol_No_Vent"] <- NA
renamed_smri_baseline[,"FS_BrainSeg_Vol_No_Vent_Surf"] <- NA
renamed_smri_baseline[,"FS_SupraTentorial_Vol_No_Vent"] <- NA
renamed_smri_baseline[,"FS_SupraTentorial_No_Vent_Voxel_Count"] <- NA
renamed_smri_baseline[,"FS_Mask_Vol"] <- NA
renamed_smri_baseline[,"FS_BrainSegVol_eTIV_Ratio"] <- NA
renamed_smri_baseline[,"FS_MaskVol_eTIV_Ratio"] <- NA
renamed_smri_baseline[,"FS_L_Vessel_Vol"] <- NA
renamed_smri_baseline[,"FS_L_ChoroidPlexus_Vol"] <- NA
renamed_smri_baseline[,"FS_R_Vessel_Vol"] <- NA
renamed_smri_baseline[,"FS_R_ChoroidPlexus_Vol"] <- NA
renamed_smri_baseline[,"FS_OpticChiasm_Vol"] <- NA
renamed_smri_baseline[,"FS_Total_GM_Vol"] <- NA


#Convert to numeric
renamed_smri_baseline[,6:ncol(renamed_smri_baseline)] <- sapply(renamed_smri_baseline[,6:ncol(renamed_smri_baseline)],as.numeric)
renamed_smri_baseline <- renamed_smri_baseline %>% 
  mutate(interview_age = as.numeric(interview_age)/12)

save(renamed_smri_baseline, file="renamed_smri_baseline.Rda")

```


```{r}
# Import Drobonin BrainAGE Model
mod_1 <- readRDS(
  file = here::here(
    "DevelopmentalBrainAge/model/xgboost_9to19_brain_age_mod.rds")) 


# Note: model1_features_baseline refers to a dataframe with columns only for interview age and brain features, named in accordance with https://github.com/GitDro/DevelopmentalBrainAge/blob/master/feature_list.txt

# check for any columns that aren't in model
names.use <- names(model1_features_baseline)[!(names(model1_features_baseline) %in% mod_1$fit$feature_names)]

# baseline
# remove those columns
model1_features_baseline_clean <- model1_features_baseline %>% 
  select(-c(FS_R_Cerebellum_Cort_Vol, interview_age))

# reorder column names to match order of feature names
newdata_baseline = as.matrix(model1_features_baseline_clean)
newdata_baseline = newdata_baseline[ , mod_1$fit$feature_names]

### Follow-Up
# remove those columns
model1_features_followup_clean <- model1_features_followup %>% 
  select(-c(FS_R_Cerebellum_Cort_Vol, interview_age))

# reorder column names to match order of feature names
newdata_followup = as.matrix(model1_features_followup_clean)
newdata_followup = newdata_followup[ , mod_1$fit$feature_names]
```


run predictions - BASELINE
```{r}

# predict brainage - baseline

# Predict
# This prediction method gives the output as a vector, we'll fix that later on
brainage_mod1_baseline <-
  mod_1$fit %>%
  predict(newdata = newdata_baseline) 

# Calculate gap
# Turn the vector into a dataframe, rename the prediction column, add back the column with chronological age, and calculate the gap
brain_age_df_mod1_baseline <- as.data.frame(brainage_mod1_baseline) %>%
  rename(.pred = brainage_mod1_baseline) %>% 
  mutate(
    # provide the chronological age at time of scan
    truth = model1_features_baseline$interview_age) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)


# bias correction
# Slope and intercept are hardcoded
bias_intercept <- 6.41 # xgb_bias_mod$coefficients[["(Intercept)"]]
bias_slope <- 0.55 # xgb_bias_mod$coefficients[["truth"]]

# create bias corrected data frame
brain_age_df_mod1_baseline_corrected <- brain_age_df_mod1_baseline %>%
  mutate(
    # corrected brain age prediction
    corrected_pred =  (.pred - bias_intercept) / bias_slope
  ) %>%
  # corrected corrected brain age gap
  mutate(corrected_gap = corrected_pred - truth)

# reattach IDs
brain_age_df_mod1_baseline_corrected$src_subject_id <- harmonized_mri_baseline$src_subject_id
```

run predictions - FOLLOW-UP
```{r}
# predict brainage - followup
brainage_mod1_followup <-
  mod_1$fit %>%
  predict(newdata = newdata_followup) 

# Calculate gap
# Turn the vector into a dataframe, rename the prediction column, add back the column with chronological age, and calculate the gap
brain_age_df_mod1_followup <- as.data.frame(brainage_mod1_followup) %>%
  rename(.pred = brainage_mod1_followup) %>% 
  mutate(
    # provide the chronological age at time of scan
    truth = model1_features_followup$interview_age) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)


# create bias corrected data frame
brain_age_df_mod1_followup_corrected <- brain_age_df_mod1_followup %>%
  mutate(
    # corrected brain age prediction
    corrected_pred =  (.pred - bias_intercept) / bias_slope
  ) %>%
  # corrected corrected brain age gap
  mutate(corrected_gap = corrected_pred - truth)

# reattach IDs
brain_age_df_mod1_followup_corrected$src_subject_id <- harmonized_mri_followup$src_subject_id
```
